NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2019-08-27 Manuscript/manuscriptPGPE.tex
Add LIPID17 POPE anad POPG data by A. Peon https://github.com/NMRLipids/MATCH/pull/61
Add data by Antonio Peon from https://github.com/NMRLipids/MATCH/pull/77/files, except the data with some unclarities: https://github.com/NMRLipids/MATCH/issues/80, https://github.com/NMRLipids/MATCH/issues/79 and https://github.com/NMRLipids/MATCH/issues/78

  \caption{List of single lipid type MD simulations without additional ions.

@@

      lipid/counter-ions & force field for lipids / ions & \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$    & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\

@@

      DPPE  & Slipids \cite{jambeck12b}    & 288 	& 9386  & 336  & 200 & 100 & \cite{slipidsDPPEfiles}  \\
      DPPE  & GROMOS-CKP    \cite{??}      & 128	& ?     & 342  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPdppe} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      POPE  & GROMOS 43A1-S3 \cite{??}     & 128	& ?     & 313  & 2$\times$200 & 2$\times$100 & \cite{gromos43a1s3POPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & CHARMM36ua \cite{??}         & 336	& ?     & 310  & 2$\times$200 & 2$\times$100 & \cite{charmm36uaPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & CHARMM36 \cite{??}           & 144	& 5760  & 310  & 500          & 400          & \cite{charmm36POPEfiles} \\
      POPE  & Slipids \cite{jambeck12b,??} & 336	& ?     & 310  & 2$\times$200 &  2$\times$100 & \cite{slipidsPOPEfiles}  \\
      POPE  & OPLS-UA vdW on H \cite{??}   & 128	& ?     & 303  & 2$\times$200 & 2$\times$100 & \cite{OPLSuaWvdWPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & OPLS-UA \cite{??}            & 128	& ?     & 303  & 2$\times$200 & 2$\times$100 & \cite{OPLSuaPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & Berger-based \cite{??}       & 128	& ?     & 303  & 2$\times$200 & 2$\times$100 & \cite{bergerPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & Berger-based2 \cite{??}      & 128	& ?     & 303  & 2$\times$200 & 2$\times$100 & \cite{berger2POPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & GROMOS-CKP    \cite{??}      & 128	& ?     & 313  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPpope} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      DOPE  & Berger-based \cite{??}       & 128	& ?     & 271  & 2$\times$200 & 2$\times$100 & \cite{bergerDOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      DOPE  & Berger-based2 \cite{??}      & 128	& ?     & 271  & 2$\times$300 & 2$\times$100 & \cite{berger2DOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      DOPE  & GROMOS-CKP    \cite{??}      & 128	& ?     & 271  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPdope} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      POPG/K$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}   & 118& 4110  & 298  & 100 & 100 & \cite{CHARMM36popg}  \\
      POPG/Na$^+$  & Slipids \cite{jambeck13}   & 288 	& 10664  & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\

@@

      DPPG/Na$^+$  & Slipids \cite{jambeck13}   & 288 	& 11232  & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
      DPPG/Na$^+$  & Slipids \cite{jambeck13}   & 288 	& 11232  & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\

@@

@@

  \caption{List of MD simulations with lipid mixtures and additional ions.

@@

      POPG             & Slipids \cite{??} \todoi{Ion parameters?}       & 0.11          & 0  & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGslipids150mMNaCl} \\
      POPG             & CHARMM36 \cite{??}        & 0.11          & 0  & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGcharmm150mMNaCl} \\
      POPE             & Slipids \cite{??} \todoi{Ion parameters?}        & 0.11          & 0  & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPEslipids150mMNaCl} \\
      POPE             & CHARMM36 \cite{??}        & 0.11          & 0  & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPEcharmm150mMNaCl} \\

>>>>

  \caption{List of MD simulations with PE lipids.

@@

      lipid/counter-ions & force field for lipids / ions  & NaCl (M) & \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$   & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\

@@

      POPE  & CHARMM36 \cite{??}           &0       & 144	& 5760  &0    & 310  & 500          & 400          & \cite{charmm36POPEfiles} \\
      POPE  & CHARMM36 \cite{??}           & 0      & 500       & 25000 & 0   &  310  & 500 & 100 & \cite{POPEcharmm} \\
      POPE  & CHARMM36 \cite{??}           & 0.11   & 500       & 25000 & 50  &  310  & 500 & 100 & \cite{POPEcharmm150mMNaCl} \\
      POPE  & CHARMM36ua \cite{??}         &0       & 336	& ?     &0    & 310  & 2$\times$200 & 2$\times$100 & \cite{charmm36uaPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      DPPE  & Slipids \cite{jambeck12b}    &0    & 288 	& 9386  &0    & 336  & 200 & 100 & \cite{slipidsDPPEfiles}  \\
      POPE  & Slipids \cite{jambeck12b,??} &0    & 336	& ?     &0    & 310  & 2$\times$200 &  2$\times$100 & \cite{slipidsPOPEfiles}  \\
      POPE  & Slipids \cite{??} \todoi{Ion parameters?}        & 0    & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPEslipids} \\
      POPE  & Slipids \cite{??} \todoi{Ion parameters?}        & 0.11 & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPEslipids150mMNaCl} \\

@@

      DPPE  & GROMOS-CKP    \cite{??}      &0    & 128	& ?     &0    & 342  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPdppe} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & GROMOS-CKP    \cite{??}      &0    & 128	& ?     &0    & 313  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPpope} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & GROMOS-CKP    \cite{??}      &0    & 500	& 25000 &0    & 310  & 500 & 100 & \cite{gromosCKPpopeT310} \\
      DOPE  & GROMOS-CKP    \cite{??}      &0    & 128	& ?     &0    & 271  & 2$\times$500 & 2$\times$400 & \cite{gromosCKPdope} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      POPE  & GROMOS 43A1-S3 \cite{??}     &0    & 128	& ?     &0    & 313  & 2$\times$200 & 2$\times$100 & \cite{gromos43a1s3POPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\

@@

      POPE  & OPLS-UA vdW on H \cite{??}   &0    & 128	& ?     &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{OPLSuaWvdWPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & OPLS-UA \cite{??}            &0    & 128	& ?     &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{OPLSuaPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & Berger-based \cite{??}       &0    & 128	& ?     &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{bergerPOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      POPE  & Berger-based2 \cite{??}      &0    & 128	& ?     &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{berger2POPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      DOPE  & Berger-based \cite{??}       &0    & 128	& ?     &0    & 271  & 2$\times$200 & 2$\times$100 & \cite{bergerDOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
      DOPE  & Berger-based2 \cite{??}      &0    & 128	& ?     &0    & 271  & 2$\times$300 & 2$\times$100 & \cite{berger2DOPEfiles} \todoi{Not analyzed yet, waiting for the code for UA simulations.}  \\
%      POPE             & LIPID17 \cite{??} & 0      & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17150mMNaCl} \\
      POPE             & LIPID17 \cite{??} & 0.11   & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17150mMNaCl} \\

@@

      \begin{table*}[htb]
  %\begin{sidewaystable*}[!p]
  \centering
  \caption{List of MD simulations with PG lipids.
    % The salt concentrations calculated as [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
    % these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
    % The lipid force fields named as in our previous work~\cite{botan15}.
  }\label{systemsII}
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{l c c r r r r r r c c}
      %\hline
      % some footnotes are not visible in typeset-MS (pdf)
      lipid/counter-ions & force field for lipids / ions & NaCl (M) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
      \hline
      POPG/K$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}    &0         & 118& 4110   &0    & 298  & 100 & 100 & \cite{CHARMM36popg}  \\
      POPG             & CHARMM36 \cite{??}        & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGcharmm150mMNaCl} \\
      POPG             & CHARMM36 \cite{??}        & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGcharmm} \\
      \hline
      POPG/Na$^+$  & Slipids \cite{jambeck13}    &0         & 288 	& 10664   &0     & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
      DPPG/Na$^+$  & Slipids \cite{jambeck13}    &0         & 288 	& 11232  &0     & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
      DPPG/Na$^+$  & Slipids \cite{jambeck13}    &0         & 288 	& 11232   &0     & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\
      POPG         & Slipids \cite{??} \todoi{Ion parameters?}       & 0    & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGslipids} \\
      POPG         & Slipids \cite{??} \todoi{Ion parameters?}       & 0.11    & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGslipids150mMNaCl} \\
      \hline
      POPG             & LIPID17 \cite{??}         & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGlipid17} \\
      POPG             & LIPID17 \cite{??}         & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGlipid17150mMNaCl} \\
      \hline
      POPG             & GROMOS-CKP \cite{??}         & 0              & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGgromosCKP} \\
      POPG             & GROMOS-CKP \cite{??}         & 0.11           & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGgromosCKP150mMNaCl} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*} 
\end{table*}

@@

  \caption{List of MD simulations with PE and PG lipids mixed with PC.

@@
